Exploitation Techniques and Mitigations

### 2016-01-14 docs/paper.tex
Paper: Add section about main assumption

>>>>

\subsection{Main Assumption}

Throughout this work we assume that we know the target binary (and the
libraries it uses). Let us show that this assumption is quite reasonable to
make by looking through the eyes of the adversary. An attacker who wants to
penetrate a target machine and get control over it would most likely choose the
easiest path, by exploiting the weakest link. Most machines relevant to an
attackers interest will run provide multiple services. For example, while the
main server of a small business company may run a homemade communication server
for interaction between them and their clients, it may also run a standard web
server. Sending a misspelled request to the server may lead following response:

\begin{pre*}{autogobble,xleftmargin=1cm}
    <!DOCTYPE HTML PUBLIC "-//IETF//DTD HTML 2.0//EN">
    <html><head>
    <title>400 Bad Request</title>
    </head><body>
    <h1>Bad Request</h1>
    <p>Your browser sent a request that this server could not understand.<br />
    </p>
    <hr>
    <address>Apache/2.2.22 (Ubuntu) Server at ovinnik.canonical.com Port 80</address>
    </body></html>
    Connection closed by foreign host.
\end{pre*}

The web server tells us his exact version and since it also provides
information about the operating system an attacker can easily copy the basic
setup to test and tweak his exploits.
